Fisheries example integrating FLR

### 2018-08-19 notebook/ms/SI5.Rmd
Definitively address Reviewer 1 minor comment 4 using the ggplotFL package

Here we closely follow [a tutorial from the FLR project](http://www.flr-project.org/doc/Modelling_stock_recruitment_with_FLSR.html). To build the stock-recruitment model, the `FLCore` package is needed [@Kell2007].

```{r, eval = FALSE}
install.packages("FLCore", repos="http://flr-project.org/R");
```

To start, we need to read in the `FLCore` and GMSE libraries.

```{r}
library(FLCore);
library(GMSE);
```

@@

Diagnostic plots, identical to those of the [modelling stock-recruitment tutorial](http://www.flr-project.org/doc/Modelling_stock_recruitment_with_FLSR.html) for the `nsher_ri` example, are shown below. We note that these plots are made using the `FLCore` package, and are not produced by, nor available in, the `GMSE` package.

>>>>

Here we closely follow [a tutorial from the FLR project](http://www.flr-project.org/doc/Modelling_stock_recruitment_with_FLSR.html). To build the stock-recruitment model, the `FLCore` package is needed [@Kell2007]. We also include the `ggplotFL` package for plotting.

```{r, eval = FALSE}
install.packages("FLCore", repos="http://flr-project.org/R");
install.packages("ggplotFL", repos="http://flr-project.org/R")
```

To start, we need to read in the `FLCore`, `ggplotFL` and `GMSE` libraries.

```{r}
library(FLCore);
library(ggplotFL);
library(GMSE);
```

@@

Diagnostic plots, identical to those of the [modelling stock-recruitment tutorial](http://www.flr-project.org/doc/Modelling_stock_recruitment_with_FLSR.html) for the `nsher_ri` example, are shown below in Figure 1. We note that these plots are made using the `FLCore` and `ggplotFL` packages, and are not produced by, nor available in, the `GMSE` package.
